---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nout

<!-- badges: start -->
<!-- badges: end -->

The goal of ***nout*** is to provide tools to quantify outliers through closed testing procedures which use conformal *p*-values. According to which local test is used, three closed testing procedures are available: Simes version, Simes version with Storey estimator for the proportion of true null hypotheses and Wilcoxon-Mann-Whitney version.

## Installation

You can install the development version of nout from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chiaragaiamagnani/nout")
```

## Example

This is a basic example which shows the use of the three main procedures contained in ***nout*** package:

```{r example}
library(nout)

set.seed(321)

# Generating score vectors
Sxy = sample(x=1:1000, size=100)
Sx = sample(Sxy, size=70)
Sy = setdiff(Sxy, Sx)

# Simes closed testing procedure
d_simes(S_Y=Sy, S_X=Sx)
# Simes with Storey closed testing procedure
d_storeysimes(S_Y=Sy, S_X=Sx)
# Wilcoxon-Mann-Whitney closed testing procedure
d_t2(S_Y=Sy, S_X=Sx, alpha=0.1)



```


<!--You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>. -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo = FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN. -->
