---
title: "Comparison between different local tests: Simes, Simes with Storey and Wilcoxon-Mann-Whitney"
output: pdf_document
date: "27-04-2023"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim is to compare on real datasets the performance of three closed testing procedures, which respectively use Simes local test with and without Storey estimator for the proportion of true null hypotheses and Wilcoxon-Mann-Whitney local test.



## R functions and libraries
```{r}
library(nout)
library(R.matlab)
library(isotree)
library(farff)
library(tictoc)




sim_realdata = function(B, dataset, m1, m, n, l, in_index, out_index=NULL, alpha=m/(l+1), lambda = 0.5){

  m0=m-m1
  if(m1!=0 & is.null(out_index)){
    stop("Error: arg out_index must be initialized.")
  }

  # if(m!=(m1+m0)){
  #   stop("Error: equation m=m1+m0 must be verified.")
  # }

  if(m1!=0){
    tr_ind = sample(in_index, size = n)
    tr = dataset[tr_ind,]
    iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=10, nthreads=1,
                              scoring_metric = "depth", output_score = TRUE)
    in_index2 = setdiff(in_index, tr_ind)

    crit=critWMW(m=m, n=n, alpha=alpha)

    d_WMW = rep(0,B)
    d_Simes = rep(0,B)
    d_StoSimes = rep(0,B)
    d_BH = rep(0,B)
    d_StoBH = rep(0,B)

    for(b in 1:B){
      cal_ind = sample(in_index2, size = l)
      in_index3 = setdiff(in_index2, cal_ind)
      tein_ind = sample(in_index3, size = m0)
      teout_ind = sample(out_index, size = m1)

      cal = dataset[cal_ind,]
      te = dataset[c(tein_ind, teout_ind),]

      S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
      S_te = predict.isolation_forest(iso.fo$model, te, type = "score")

      d_WMW[b] = d_mannwhitney(S_X=S_cal, S_Y=S_te, crit=crit)
      d_Simes[b] = d_Simes(S_X=S_cal, S_Y=S_te, alpha=alpha)
      d_StoSimes[b] = d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=alpha)
      d_BH[b] = d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=alpha)
      d_StoBH[b] = d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=alpha)
    }
  }

  else{
    tr_ind = sample(in_index, size = n)
    tr = dataset[tr_ind,]
    iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=10, nthreads=1,
                              scoring_metric = "depth", output_score = TRUE)
    in_index2 = setdiff(in_index, tr_ind)

    crit=critWMW(m=m, n=n, alpha=alpha)

    d_WMW = rep(0,B)
    d_Simes = rep(0,B)
    d_StoSimes = rep(0,B)
    d_BH = rep(0,B)
    d_StoBH = rep(0,B)

    for(b in 1:B){
      cal_ind = sample(in_index2, size = l)
      in_index3 = setdiff(in_index2, cal_ind)
      te_ind = sample(in_index3, size = m0)

      cal = dataset[cal_ind,]
      te = dataset[te_ind,]

      S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
      S_te = predict.isolation_forest(iso.fo$model, te, type = "score")

      d_WMW[b] = d_mannwhitney(S_X=S_cal, S_Y=S_te, crit=crit)
      d_Simes[b] = d_Simes(S_X=S_cal, S_Y=S_te, alpha=alpha)
      d_StoSimes[b] = d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=alpha)
      d_BH[b] = d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=alpha)
      d_StoBH[b] = d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=alpha)
    }
  }

  discov = as.data.frame(cbind("d_BH"=d_BH, "d_StoBH"=d_StoBH, "d_Simes"=d_Simes,
                               "d_StoSimes"=d_StoSimes, "d_WMW"=d_WMW))
  colnames(discov) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
  mean.discov = apply(discov, MARGIN = 2, FUN = mean)

  powerGlobalNull = as.data.frame(cbind("d_BH"=d_BH>0, "d_StoBH"=d_StoBH>0, "d_Simes"=d_Simes>0,
                                        "d_StoSimes"=d_StoSimes>0, "d_WMW"=d_WMW>0))
  colnames(powerGlobalNull) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
  mean.powerGlobalNull = apply(powerGlobalNull, MARGIN = 2, FUN = mean)

  return(list("discoveries"=discov, "mean.discoveries" = mean.discov,
              "powerGlobalNull"=powerGlobalNull, "mean.powerGlobalNull"=mean.powerGlobalNull,
              "m1"=m1, "alpha"=alpha))

}


```



In the following we set the calibration set and the test set size, respectively $l$ and $m$, so that the nominal level $\alpha$ is proportional to $\frac{m}{l+1}$. The train set size is equal to $n$ and the number of iterations is $B=10^3$.



## Statlog (Shuttle) dataset
The dataset is available at http://odds.cs.stonybrook.edu/shuttle-dataset

```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
B=10^3
n = 199
l = 199
m = 20
alpha = m/(l+1)
m1s = seq(from=0, to=m, by=1)

data = readMat("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset shuttle\\shuttle.mat")
dataset = cbind(data$X, data$y); colnames(dataset)[ncol(dataset)] = "y"
in_ind = which(dataset[,ncol(dataset)]==0)
out_ind = which(dataset[,ncol(dataset)]==1)

tic()
res = lapply(m1s,
             function(m1) sim_realdata(B=B, in_index=in_ind, out_index=out_ind,
                                       dataset=dataset,
                                       alpha=alpha,l=l, n=n, m=m, m1=m1))
toc()

# Storing results
store_res = list("mean.discov" = matrix(nrow=length(m1s), ncol = 5),
                 "mean.powerGlobalNull" = matrix(nrow=length(m1s), ncol = 5))
row.names = rep(NA, times=length(m1s))
for(i in 1:length(m1s)){
  row.names[i] = paste("m1 =",m1s[i])
}
rownames(store_res$mean.discov) = row.names
colnames(store_res$mean.discov) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")
rownames(store_res$mean.powerGlobalNull) = row.names
colnames(store_res$mean.powerGlobalNull) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")


for(i in 1:length(res)){
  store_res$mean.discov[i,] = res[[i]]$mean.discov
  store_res$mean.powerGlobalNull[i,] = res[[i]]$mean.powerGlobalNull
}

store_res$mean.discov
store_res$mean.powerGlobalNull

plot(x = m1s, y = store_res$mean.discov[,1], col = 1, ylab = "d",
     xlab = "m1", ylim=c(0,m), pch=19,
     main = "Mean of the number of discoveries on B replications")
points(x = m1s, y = store_res$mean.discov[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.discov[,5], col = 5, pch=19)
legend("bottomleft", pch = 19, col = c(1,2,5),
       legend =c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))


plot(x = m1s, y = store_res$mean.powerGlobalNull[,1], col = 1, ylab = "power",
     xlab = "m1", ylim=c(0,1), pch = 19,
     main = "Mean of the power on B replications")
points(x = m1s, y = store_res$mean.powerGlobalNull[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.powerGlobalNull[,5], col = 5, pch=19)
legend("bottomright", pch = 19, col = c(1,2,5),
       legend = c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))



```








## Credit Card Fraud Detection dataset
The dataset is available at  https://www.kaggle.com/mlg-ulb/creditcardfraud.

```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
B=10^3
n = 199
l = 199
m = 20
alpha = m/(l+1)
m1s = seq(from=0, to=m, by=1)

dataset = read.csv("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset creditcard\\creditcard.csv")
in_ind = which(dataset[,ncol(dataset)]==0)
out_ind = which(dataset[,ncol(dataset)]==1)

tic()
res = lapply(m1s,
             function(m1) sim_realdata(B=B, in_index=in_ind, out_index=out_ind,
                                       dataset=dataset,
                                       alpha=alpha,l=l, n=n, m=m, m1=m1))
toc()

# Storing results
store_res = list("mean.discov" = matrix(nrow=length(m1s), ncol = 5),
                 "mean.powerGlobalNull" = matrix(nrow=length(m1s), ncol = 5))
row.names = rep(NA, times=length(m1s))
for(i in 1:length(m1s)){
  row.names[i] = paste("m1 =",m1s[i])
}
rownames(store_res$mean.discov) = row.names
colnames(store_res$mean.discov) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")
rownames(store_res$mean.powerGlobalNull) = row.names
colnames(store_res$mean.powerGlobalNull) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")


for(i in 1:length(res)){
  store_res$mean.discov[i,] = res[[i]]$mean.discov
  store_res$mean.powerGlobalNull[i,] = res[[i]]$mean.powerGlobalNull
}

store_res$mean.discov
store_res$mean.powerGlobalNull

plot(x = m1s, y = store_res$mean.discov[,1], col = 1, ylab = "d",
     xlab = "m1", ylim=c(0,m), pch=19,
     main = "Mean of the number of discoveries on B replications")
points(x = m1s, y = store_res$mean.discov[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.discov[,5], col = 5, pch=19)
legend("bottomleft", pch = 19, col = c(1,2,5),
       legend =c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))


plot(x = m1s, y = store_res$mean.powerGlobalNull[,1], col = 1, ylab = "power",
     xlab = "m1", ylim=c(0,1), pch = 19,
     main = "Mean of the power on B replications")
points(x = m1s, y = store_res$mean.powerGlobalNull[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.powerGlobalNull[,5], col = 5, pch=19)
legend("bottomright", pch = 19, col = c(1,2,5),
       legend = c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))



```



## Covertype dataset
The dataset is available at http://odds.cs.stonybrook.edu/forestcovercovertype-dataset.

```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
B=10^3
n = 199
l = 199
m = 20
alpha = m/(l+1)
m1s = seq(from=0, to=m, by=1)

data = readMat("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset shuttle\\shuttle.mat")
dataset = cbind(data$X, data$y); colnames(dataset)[ncol(dataset)] = "y"
in_ind = which(dataset[,ncol(dataset)]==0)
out_ind = which(dataset[,ncol(dataset)]==1)

tic()
res = lapply(m1s,
             function(m1) sim_realdata(B=B, in_index=in_ind, out_index=out_ind,
                                       dataset=dataset,
                                       alpha=alpha,l=l, n=n, m=m, m1=m1))
toc()

# Storing results
store_res = list("mean.discov" = matrix(nrow=length(m1s), ncol = 5),
                 "mean.powerGlobalNull" = matrix(nrow=length(m1s), ncol = 5))
row.names = rep(NA, times=length(m1s))
for(i in 1:length(m1s)){
  row.names[i] = paste("theta =",m1s[i])
}
rownames(store_res$mean.discov) = row.names
colnames(store_res$mean.discov) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")
rownames(store_res$mean.powerGlobalNull) = row.names
colnames(store_res$mean.powerGlobalNull) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")


for(i in 1:length(res)){
  store_res$mean.discov[i,] = res[[i]]$mean.discov
  store_res$mean.powerGlobalNull[i,] = res[[i]]$mean.powerGlobalNull
}

store_res$mean.discov
store_res$mean.powerGlobalNull

plot(x = m1s, y = store_res$mean.discov[,1], col = 1, ylab = "d",
     xlab = "m1", ylim=c(0,m), pch=19,
     main = "Mean of the number of discoveries on B replications")
points(x = m1s, y = store_res$mean.discov[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.discov[,5], col = 5, pch=19)
legend("bottomleft", pch = 19, col = c(1,2,5),
       legend =c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))


plot(x = m1s, y = store_res$mean.powerGlobalNull[,1], col = 1, ylab = "power",
     xlab = "m1", ylim=c(0,1), pch = 19,
     main = "Mean of the power on B replications")
points(x = m1s, y = store_res$mean.powerGlobalNull[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.powerGlobalNull[,5], col = 5, pch=19)
legend("bottomright", pch = 19, col = c(1,2,5),
       legend = c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))



```




## Mammography dataset
The dataset is available at http://odds.cs.stonybrook.edu/mammography-dataset/.

```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
B=10^3
n = 199
l = 199
m = 20
alpha = m/(l+1)
m1s = seq(from=0, to=m, by=1)
data = readMat("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset mammography\\mammography.mat")
dataset = cbind(data$X, data$y); colnames(dataset)[ncol(dataset)] = "y"
in_ind = which(dataset[,ncol(dataset)]==0)
out_ind = which(dataset[,ncol(dataset)]==1)

tic()
res = lapply(m1s,
             function(m1) sim_realdata(B=B, in_index=in_ind, out_index=out_ind,
                                       dataset=dataset,
                                       alpha=alpha,l=l, n=n, m=m, m1=m1))
toc()

# Storing results
store_res = list("mean.discov" = matrix(nrow=length(m1s), ncol = 5),
                 "mean.powerGlobalNull" = matrix(nrow=length(m1s), ncol = 5))
row.names = rep(NA, times=length(m1s))
for(i in 1:length(m1s)){
  row.names[i] = paste("theta =",m1s[i])
}
rownames(store_res$mean.discov) = row.names
colnames(store_res$mean.discov) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")
rownames(store_res$mean.powerGlobalNull) = row.names
colnames(store_res$mean.powerGlobalNull) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")


for(i in 1:length(res)){
  store_res$mean.discov[i,] = res[[i]]$mean.discov
  store_res$mean.powerGlobalNull[i,] = res[[i]]$mean.powerGlobalNull
}

store_res$mean.discov
store_res$mean.powerGlobalNull

plot(x = m1s, y = store_res$mean.discov[,1], col = 1, ylab = "d",
     xlab = "m1", ylim=c(0,m), pch=19,
     main = "Mean of the number of discoveries on B replications")
points(x = m1s, y = store_res$mean.discov[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.discov[,5], col = 5, pch=19)
legend("bottomleft", pch = 19, col = c(1,2,5),
       legend =c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))


plot(x = m1s, y = store_res$mean.powerGlobalNull[,1], col = 1, ylab = "power",
     xlab = "m1", ylim=c(0,1), pch = 19,
     main = "Mean of the power on B replications")
points(x = m1s, y = store_res$mean.powerGlobalNull[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.powerGlobalNull[,5], col = 5, pch=19)
legend("bottomright", pch = 19, col = c(1,2,5),
       legend = c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))



```



## Pen-Based Recognition of Handwritten Digits dataset
The dataset is available at http://odds.cs.stonybrook.edu/pendigits-dataset. 

```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
B=10^3
n = 199
l = 199
m = 20
alpha = m/(l+1)
m1s = seq(from=0, to=m, by=1)

data = readMat("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset digits\\pendigits.mat")
dataset = cbind(data$X, data$y); colnames(dataset)[ncol(dataset)] = "y"
in_ind = which(dataset[,ncol(dataset)]==0)
out_ind = which(dataset[,ncol(dataset)]==1)

tic()
res = lapply(m1s,
             function(m1) sim_realdata(B=B, in_index=in_ind, out_index=out_ind,
                                       dataset=dataset,
                                       alpha=alpha,l=l, n=n, m=m, m1=m1))
toc()

# Storing results
store_res = list("mean.discov" = matrix(nrow=length(m1s), ncol = 5),
                 "mean.powerGlobalNull" = matrix(nrow=length(m1s), ncol = 5))
row.names = rep(NA, times=length(m1s))
for(i in 1:length(m1s)){
  row.names[i] = paste("theta =",m1s[i])
}
rownames(store_res$mean.discov) = row.names
colnames(store_res$mean.discov) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")
rownames(store_res$mean.powerGlobalNull) = row.names
colnames(store_res$mean.powerGlobalNull) = c("BH", "StoBH", "Simes", "StoSimes", "WMW")


for(i in 1:length(res)){
  store_res$mean.discov[i,] = res[[i]]$mean.discov
  store_res$mean.powerGlobalNull[i,] = res[[i]]$mean.powerGlobalNull
}

store_res$mean.discov
store_res$mean.powerGlobalNull

plot(x = m1s, y = store_res$mean.discov[,1], col = 1, ylab = "d",
     xlab = "m1", ylim=c(0,m), pch=19,
     main = "Mean of the number of discoveries on B replications")
points(x = m1s, y = store_res$mean.discov[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.discov[,5], col = 5, pch=19)
legend("bottomleft", pch = 19, col = c(1,2,5),
       legend =c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))


plot(x = m1s, y = store_res$mean.powerGlobalNull[,1], col = 1, ylab = "power",
     xlab = "m1", ylim=c(0,1), pch = 19,
     main = "Mean of the power on B replications")
points(x = m1s, y = store_res$mean.powerGlobalNull[,2], col = 2, pch=19)
points(x = m1s, y = store_res$mean.powerGlobalNull[,5], col = 5, pch=19)
legend("bottomright", pch = 19, col = c(1,2,5),
       legend = c("BH and Simes CT", "StoreyBH and StoreySimes CT", "WMW CT"))



```










