---
title: "Real Data Power Analysis"
author: "Significance level 0.2"
output: pdf_document
date: '`r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(nout)
library(R.matlab)
library(isotree)
library(tictoc)

```


The aim is to compare on Digits, Credit Card and Shuttle datasets the performance of three closed testing procedures, which respectively use Simes local test with and without Storey estimator for the proportion of true null hypotheses and Wilcoxon-Mann-Whitney local test.

We fix the train set on which we train the isolation forest algorithm and we generate $B=10^4$ calibration and test sets. For each $b=1,\ldots,B$ we compute the number of discoveries obtained by Benjamini-Hochberg procedure with and without Storey's estimator for the proportion of true null hypotheses, by closed testing using Simes local test with and without Storey's estimator and by closed testing using Wilcoxon-Mann-Whitney local test.


## Digits dataset
Digits dataset (available at http://odds.cs.stonybrook.edu/pendigits-dataset) consists of $6870$ observations, among which $n_{inliers}=6714$ items are inliers and the remaining $n_{outliers}=156$ are outliers.
We will denote by $n,l,m$ respectively the train set, the calibration set and the test set size. And reproducing the same setting as in [1], we have that $m+n=n_{inliers}/2$, $m=min\{2000,l/2\}$ and $n=min\{2000, l/3\}$. 
In the case of Digits dataset we obtain
$$m+n=6714/2, \hspace{2mm} m=l/3,  \hspace{2mm} n=l/3$$
from which $n=2517.75, \hspace{2mm} l=839.25, \hspace{2mm} m=839.25$. Arbitrarily, we choose to set 
$$n=1258, \hspace{2mm} l=2099, \hspace{2mm} m=420$$ in order to have exact control of  type I errors at the significance level $\alpha=0.2.$


Load the data and set the parameters as described above.

```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
l = 2518
m = 2099
n = 420
myalpha = n/(m+1)

data = readMat("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset digits\\pendigits.mat")
dataset = cbind(data$X, data$y); colnames(dataset)[ncol(dataset)] = "y"
in_ind = which(dataset[,ncol(dataset)]==0)
out_ind = which(dataset[,ncol(dataset)]==1)


```





### All inliers
We now set the proportion of inliers equal to $1$, so that the number of outliers $n_1=0$.
```{r warning=FALSE, message=FALSE}
B=10^4

n1=0
n0=n-n1

tr_ind = sample(in_ind, size = l)
tr = dataset[tr_ind,]
iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=100, nthreads=parallel::detectCores(),
                          scoring_metric = "depth", output_score = TRUE)
in_index2 = setdiff(in_ind, tr_ind)
mycrit = nout::critWMW(m=n,n=m,alpha=myalpha)
    
d_WMW = rep(0,B)
d_Simes = rep(0,B)
d_StoSimes = rep(0,B)
d_BH = rep(0,B)
d_StoBH = rep(0,B)
resU = rep(0,B)
    
for (b in 1:B){
  cal_ind = sample(in_index2, size = m)
  in_index3 = setdiff(in_index2, cal_ind)
  te_ind = sample(in_index3, size = n)
  cal = dataset[cal_ind,]
  te = dataset[te_ind,]
      
  S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
  S_te = predict.isolation_forest(iso.fo$model, te, type = "score")
  U_i = sapply(1:n, function(i) sum(S_te[i]>S_cal))
  U = sum(U_i)
      
  d_WMW[b] = nout::d_mannwhitney(S_Y=S_te, S_X=S_cal, crit = mycrit)
  resU[b] = U >=mycrit$crit.vals[1]
  d_Simes[b] = nout::d_Simes(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoSimes[b] = nout::d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=myalpha)$d
  d_BH[b] = nout::d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoBH[b] = nout::d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=myalpha)
}

 
discoveries = as.data.frame(cbind("d_BH"=d_BH, "d_StoBH"=d_StoBH, "d_Simes"=d_Simes,
                               "d_StoSimes"=d_StoSimes, "d_WMW"=d_WMW))
colnames(discoveries) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.discoveries = apply(discoveries, MARGIN = 2, FUN = mean)
  
powerGlobalNull = as.data.frame(cbind("d_BH"=d_BH>0, "d_StoBH"=d_StoBH>0, "d_Simes"=d_Simes>0,
                                        "d_StoSimes"=d_StoSimes>0, "d_WMW"=d_WMW>0))
colnames(powerGlobalNull) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.powerGlobalNull = apply(powerGlobalNull, MARGIN = 2, FUN = mean)

prova.d_WMW = mean(d_WMW>0)
prova.resU = mean(resU)
  

boxplot(discoveries, main="Digits | Distribution of the number of discoveries")
points(x=1:5, y=mean.discoveries, pch=19, col="red")
mean.discoveries
mean.powerGlobalNull
prova.d_WMW
prova.resU

res=list("prova.d_WMW"=prova.d_WMW, 
         "prova.resU"=prova.resU, 
         "resU" = resU, 
         "discoveries"=discoveries,
         "mean.discoveries" = mean.discoveries, 
         "powerGlobalNull"=powerGlobalNull,
         "mean.powerGlobalNull"=mean.powerGlobalNull, 
         "n1"=n1, 
         "alpha"=alpha)

resDigits0 = res
save(resDigits0,
     file="C:/Users/c.magnani9/Documents/nout/trials/RealData/PowerStudy/New&TidyNoSimuFunction/alpha0.2/resDigits0")

```




### 10% outliers
We now set the proportion of inliers equal to $0.9$. Referring to Digits dataset we have that the number of inliers is $n_0=378$ and the number of outliers is $n_1=42$.

```{r warning=FALSE, message=FALSE}
B=10^4

n1=round(0.1*n)
n0=n-n1

tr_ind = sample(in_ind, size = l)
tr = dataset[tr_ind,]
iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=10, nthreads=parallel::detectCores()-1L,
                          scoring_metric = "depth", output_score = TRUE)
in_index2 = setdiff(in_ind, tr_ind)
mycrit = nout::critWMW(m=n,n=m,alpha=myalpha)
    
d_WMW = rep(0,B)
d_Simes = rep(0,B)
d_StoSimes = rep(0,B)
d_BH = rep(0,B)
d_StoBH = rep(0,B)
resU = rep(0,B)
    
for (b in 1:B){
  cal_ind = sample(in_index2, size = m)
  in_index3 = setdiff(in_index2, cal_ind)
  tein_ind = sample(in_index3, size = n0)
  teout_ind = sample(out_index, size = n1)
  cal = dataset[cal_ind,]
  te = dataset[c(tein_ind, teout_ind),]
      
  S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
  S_te = predict.isolation_forest(iso.fo$model, te, type = "score")
  U_i = sapply(1:n, function(i) sum(S_te[i]>S_cal))
  U = sum(U_i)
      
  d_WMW[b] = nout::d_mannwhitney(S_Y=S_te, S_X=S_cal, crit = mycrit)
  resU[b] = U >=mycrit$crit.vals[1]
  d_Simes[b] = nout::d_Simes(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoSimes[b] = nout::d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=myalpha)$d
  d_BH[b] = nout::d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoBH[b] = nout::d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=myalpha)
}

 
discoveries = as.data.frame(cbind("d_BH"=d_BH, "d_StoBH"=d_StoBH, "d_Simes"=d_Simes,
                               "d_StoSimes"=d_StoSimes, "d_WMW"=d_WMW))
colnames(discoveries) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.discoveries = apply(discoveries, MARGIN = 2, FUN = mean)
  
powerGlobalNull = as.data.frame(cbind("d_BH"=d_BH>0, "d_StoBH"=d_StoBH>0, "d_Simes"=d_Simes>0,
                                        "d_StoSimes"=d_StoSimes>0, "d_WMW"=d_WMW>0))
colnames(powerGlobalNull) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.powerGlobalNull = apply(powerGlobalNull, MARGIN = 2, FUN = mean)

prova.d_WMW = mean(d_WMW>0)
prova.resU = mean(resU)
  

boxplot(discoveries, main="Digits | Distribution of the number of discoveries")
points(x=1:5, y=mean.discoveries, pch=19, col="red")
mean.discoveries
mean.powerGlobalNull
prova.d_WMW
prova.resU

res=list("prova.d_WMW"=prova.d_WMW, 
         "prova.resU"=prova.resU, 
         "resU" = resU, 
         "discoveries"=discoveries,
         "mean.discoveries" = mean.discoveries, 
         "powerGlobalNull"=powerGlobalNull,
         "mean.powerGlobalNull"=mean.powerGlobalNull, 
         "n1"=n1, 
         "alpha"=alpha)

resDigits10 = res
save(resDigits10,
     file="C:/Users/c.magnani9/Documents/nout/trials/RealData/PowerStudy/New&TidyNoSimuFunction/alpha0.2/resDigits10")

```






## Credit Card Fraud Detection dataset
Credit card dataset (available at https://www.kaggle.com/mlg-ulb/creditcardfraud) consists of $284807$ observations, among which $n_{inliers}=284315$ items are inliers and the remaining $n_{outliers}=492$ are outliers.

In the case of Credit Card dataset we obtain
$$m+n=284315/2, \hspace{2mm} m=2000,  \hspace{2mm} n=2000.$$
Arbitrarily, we choose to set 
$$l=132158, \hspace{2mm} m=9999, \hspace{2mm} n=2000$$ in order to have exact control of  type I errors at the significance level $\alpha=0.2.$

Load the data and set the parameters ad described above.

```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
l = 132158
m = 9999
n = 2000
myalpha = 0.2

dataset = read_csv("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset creditcard\\creditcard.csv")
out_ind = which(dataset$Class==1)
in_ind = which(dataset$Class==0)

```





### All inliers
We now set the proportion of inliers equal to $1$, so that the number of outliers $n_1=0$.
```{r warning=FALSE, message=FALSE}
B=10^4

n1=0
n0=n-n1

tr_ind = sample(in_ind, size = l)
tr = dataset[tr_ind,]
iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=10, sample_size = 256, nthreads=parallel::detectCores()-1L,
                          scoring_metric = "depth", output_score = TRUE)
in_index2 = setdiff(in_ind, tr_ind)
mycrit = nout::critWMW(m=n,n=m,alpha=myalpha)
    
d_WMW = rep(0,B)
d_Simes = rep(0,B)
d_StoSimes = rep(0,B)
d_BH = rep(0,B)
d_StoBH = rep(0,B)
resU = rep(0,B)
    
for (b in 1:B){
  cal_ind = sample(in_index2, size = m)
  in_index3 = setdiff(in_index2, cal_ind)
  te_ind = sample(in_index3, size = n)
  cal = dataset[cal_ind,]
  te = dataset[te_ind,]
      
  S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
  S_te = predict.isolation_forest(iso.fo$model, te, type = "score")
  U_i = sapply(1:n, function(i) sum(S_te[i]>S_cal))
  U = sum(U_i)
      
  d_WMW[b] = nout::d_mannwhitney(S_Y=S_te, S_X=S_cal, crit = mycrit)
  resU[b] = U >=mycrit$crit.vals[1]
  d_Simes[b] = nout::d_Simes(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoSimes[b] = nout::d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=myalpha)$d
  d_BH[b] = nout::d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoBH[b] = nout::d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=myalpha)
}

 
discoveries = as.data.frame(cbind("d_BH"=d_BH, "d_StoBH"=d_StoBH, "d_Simes"=d_Simes,
                               "d_StoSimes"=d_StoSimes, "d_WMW"=d_WMW))
colnames(discoveries) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.discoveries = apply(discoveries, MARGIN = 2, FUN = mean)
  
powerGlobalNull = as.data.frame(cbind("d_BH"=d_BH>0, "d_StoBH"=d_StoBH>0, "d_Simes"=d_Simes>0,
                                        "d_StoSimes"=d_StoSimes>0, "d_WMW"=d_WMW>0))
colnames(powerGlobalNull) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.powerGlobalNull = apply(powerGlobalNull, MARGIN = 2, FUN = mean)

prova.d_WMW = mean(d_WMW>0)
prova.resU = mean(resU)
  

boxplot(discoveries, main="Digits | Distribution of the number of discoveries")
points(x=1:5, y=mean.discoveries, pch=19, col="red")
mean.discoveries
mean.powerGlobalNull
prova.d_WMW
prova.resU

res=list("prova.d_WMW"=prova.d_WMW, 
         "prova.resU"=prova.resU, 
         "resU" = resU, 
         "discoveries"=discoveries,
         "mean.discoveries" = mean.discoveries, 
         "powerGlobalNull"=powerGlobalNull,
         "mean.powerGlobalNull"=mean.powerGlobalNull, 
         "n1"=n1, 
         "alpha"=alpha)

resCredit0 = res
save(resCredit0,
     file="C:/Users/c.magnani9/Documents/nout/trials/RealData/PowerStudy/New&TidyNoSimuFunction/alpha0.2/resCredit0")

```




### 10% outliers
We now set the proportion of inliers equal to $0.9$. Referring to Credit Card dataset we have that the number of inliers is $n_0=1800$ and the number of outliers is $n_1=200$.

```{r warning=FALSE, message=FALSE}
B=10^4

n1=round(0.1*n)
n0=n-n1

tr_ind = sample(in_ind, size = l)
tr = dataset[tr_ind,]
iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=10, sample_size = 256, nthreads=parallel::detectCores()-1L,
                          scoring_metric = "depth", output_score = TRUE)
in_index2 = setdiff(in_ind, tr_ind)
mycrit = nout::critWMW(m=n,n=m,alpha=myalpha)
    
d_WMW = rep(0,B)
d_Simes = rep(0,B)
d_StoSimes = rep(0,B)
d_BH = rep(0,B)
d_StoBH = rep(0,B)
resU = rep(0,B)
    
for (b in 1:B){
  cal_ind = sample(in_index2, size = m)
  in_index3 = setdiff(in_index2, cal_ind)
  tein_ind = sample(in_index3, size = n0)
  teout_ind = sample(out_index, size = n1)
  cal = dataset[cal_ind,]
  te = dataset[c(tein_ind, teout_ind),]
      
  S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
  S_te = predict.isolation_forest(iso.fo$model, te, type = "score")
  U_i = sapply(1:n, function(i) sum(S_te[i]>S_cal))
  U = sum(U_i)
      
  d_WMW[b] = nout::d_mannwhitney(S_Y=S_te, S_X=S_cal, crit = mycrit)
  resU[b] = U >=mycrit$crit.vals[1]
  d_Simes[b] = nout::d_Simes(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoSimes[b] = nout::d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=myalpha)$d
  d_BH[b] = nout::d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoBH[b] = nout::d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=myalpha)
}

 
discoveries = as.data.frame(cbind("d_BH"=d_BH, "d_StoBH"=d_StoBH, "d_Simes"=d_Simes,
                               "d_StoSimes"=d_StoSimes, "d_WMW"=d_WMW))
colnames(discoveries) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.discoveries = apply(discoveries, MARGIN = 2, FUN = mean)
  
powerGlobalNull = as.data.frame(cbind("d_BH"=d_BH>0, "d_StoBH"=d_StoBH>0, "d_Simes"=d_Simes>0,
                                        "d_StoSimes"=d_StoSimes>0, "d_WMW"=d_WMW>0))
colnames(powerGlobalNull) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.powerGlobalNull = apply(powerGlobalNull, MARGIN = 2, FUN = mean)

prova.d_WMW = mean(d_WMW>0)
prova.resU = mean(resU)
  

boxplot(discoveries, main="Digits | Distribution of the number of discoveries")
points(x=1:5, y=mean.discoveries, pch=19, col="red")
mean.discoveries
mean.powerGlobalNull
prova.d_WMW
prova.resU

res=list("prova.d_WMW"=prova.d_WMW, 
         "prova.resU"=prova.resU, 
         "resU" = resU, 
         "discoveries"=discoveries,
         "mean.discoveries" = mean.discoveries, 
         "powerGlobalNull"=powerGlobalNull,
         "mean.powerGlobalNull"=mean.powerGlobalNull, 
         "n1"=n1, 
         "alpha"=alpha)

resCredit10 = res
save(resCredit10,
     file="C:/Users/c.magnani9/Documents/nout/trials/RealData/PowerStudy/New&TidyNoSimuFunction/alpha0.2/resCredit10")

```






## Statlog (Shuttle) dataset
Shuttle dataset (available at http://odds.cs.stonybrook.edu/shuttle-dataset) consists of $49097$ observations, among which $n_{inliers}=45586$ items are inliers and the remaining $n_{outliers}=3511$ are outliers.
In the case of Digits dataset we obtain
$$m+n=45586/2, \hspace{2mm} m=2000,  \hspace{2mm} n=2000$$
Arbitrarily, we choose to set 
$$l=12794, \hspace{2mm} m=9999, \hspace{2mm} n=2000$$ in order to have exact control of  type I errors at the significance level $\alpha=0.2.$

Load the data and set the parameters ad described above.




```{r warning=FALSE, message=FALSE}
set.seed(321)

# Initializing parameters
l = 12794
m = 9999
n = 2000
myalpha = 0.2

data = readMat("G:\\Il mio Drive\\PHD\\Progetto di ricerca\\Conformal Inference Project\\Simulazioni\\7. Applicazioni dati reali\\Dataset shuttle\\shuttle.mat")
dataset = cbind(data$X, data$y); colnames(dataset)[ncol(dataset)] = "y"
out_ind = which(dataset[,ncol(dataset)]==1)
in_ind = which(dataset[,ncol(dataset)]==0)


```





### All inliers
We now set the proportion of inliers equal to $1$, so that the number of outliers $n_1=0$.

```{r warning=FALSE, message=FALSE}
B=10^4

n1=0
n0=n-n1

tr_ind = sample(in_ind, size = l)
tr = dataset[tr_ind,]
iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=10, sample_size = 256, nthreads=parallel::detectCores()-1L,
                          scoring_metric = "depth", output_score = TRUE)
in_index2 = setdiff(in_ind, tr_ind)
mycrit = nout::critWMW(m=n,n=m,alpha=myalpha)
    
d_WMW = rep(0,B)
d_Simes = rep(0,B)
d_StoSimes = rep(0,B)
d_BH = rep(0,B)
d_StoBH = rep(0,B)
resU = rep(0,B)
    
for (b in 1:B){
  cal_ind = sample(in_index2, size = m)
  in_index3 = setdiff(in_index2, cal_ind)
  te_ind = sample(in_index3, size = n)
  cal = dataset[cal_ind,]
  te = dataset[te_ind,]
      
  S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
  S_te = predict.isolation_forest(iso.fo$model, te, type = "score")
  U_i = sapply(1:n, function(i) sum(S_te[i]>S_cal))
  U = sum(U_i)
      
  d_WMW[b] = nout::d_mannwhitney(S_Y=S_te, S_X=S_cal, crit = mycrit)
  resU[b] = U >=mycrit$crit.vals[1]
  d_Simes[b] = nout::d_Simes(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoSimes[b] = nout::d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=myalpha)$d
  d_BH[b] = nout::d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoBH[b] = nout::d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=myalpha)
}

 
discoveries = as.data.frame(cbind("d_BH"=d_BH, "d_StoBH"=d_StoBH, "d_Simes"=d_Simes,
                               "d_StoSimes"=d_StoSimes, "d_WMW"=d_WMW))
colnames(discoveries) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.discoveries = apply(discoveries, MARGIN = 2, FUN = mean)
  
powerGlobalNull = as.data.frame(cbind("d_BH"=d_BH>0, "d_StoBH"=d_StoBH>0, "d_Simes"=d_Simes>0,
                                        "d_StoSimes"=d_StoSimes>0, "d_WMW"=d_WMW>0))
colnames(powerGlobalNull) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.powerGlobalNull = apply(powerGlobalNull, MARGIN = 2, FUN = mean)

prova.d_WMW = mean(d_WMW>0)
prova.resU = mean(resU)
  

boxplot(discoveries, main="Digits | Distribution of the number of discoveries")
points(x=1:5, y=mean.discoveries, pch=19, col="red")
mean.discoveries
mean.powerGlobalNull
prova.d_WMW
prova.resU

res=list("prova.d_WMW"=prova.d_WMW, 
         "prova.resU"=prova.resU, 
         "resU" = resU, 
         "discoveries"=discoveries,
         "mean.discoveries" = mean.discoveries, 
         "powerGlobalNull"=powerGlobalNull,
         "mean.powerGlobalNull"=mean.powerGlobalNull, 
         "n1"=n1, 
         "alpha"=alpha)

resShuttle0 = res
save(resShuttle0,
     file="C:/Users/c.magnani9/Documents/nout/trials/RealData/PowerStudy/New&TidyNoSimuFunction/alpha0.2/resShuttle0")

```





### 10% outliers
We now set the proportion of inliers equal to $0.9$. Referring to Shuttle dataset we have that the number of inliers is $n_0=1800$ and the number of outliers is $n_1=200$.

```{r warning=FALSE, message=FALSE}
B=10^4

n1=round(0.1*n)
n0=n-n1

tr_ind = sample(in_ind, size = l)
tr = dataset[tr_ind,]
iso.fo = isolation.forest(tr, ndim=ncol(dataset), ntrees=10, sample_size = 256, nthreads=parallel::detectCores()-1L,
                          scoring_metric = "depth", output_score = TRUE)
in_index2 = setdiff(in_ind, tr_ind)
mycrit = nout::critWMW(m=n,n=m,alpha=myalpha)
    
d_WMW = rep(0,B)
d_Simes = rep(0,B)
d_StoSimes = rep(0,B)
d_BH = rep(0,B)
d_StoBH = rep(0,B)
resU = rep(0,B)
    
for (b in 1:B){
  cal_ind = sample(in_index2, size = m)
  in_index3 = setdiff(in_index2, cal_ind)
  tein_ind = sample(in_index3, size = n0)
  teout_ind = sample(out_index, size = n1)
  cal = dataset[cal_ind,]
  te = dataset[c(tein_ind, teout_ind),]
      
  S_cal = predict.isolation_forest(iso.fo$model, cal, type = "score")
  S_te = predict.isolation_forest(iso.fo$model, te, type = "score")
  U_i = sapply(1:n, function(i) sum(S_te[i]>S_cal))
  U = sum(U_i)
      
  d_WMW[b] = nout::d_mannwhitney(S_Y=S_te, S_X=S_cal, crit = mycrit)
  resU[b] = U >=mycrit$crit.vals[1]
  d_Simes[b] = nout::d_Simes(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoSimes[b] = nout::d_StoreySimes(S_X=S_cal, S_Y=S_te, alpha=myalpha)$d
  d_BH[b] = nout::d_benjhoch(S_X=S_cal, S_Y=S_te, alpha=myalpha)
  d_StoBH[b] = nout::d_StoreyBH(S_X=S_cal, S_Y=S_te, alpha=myalpha)
}

 
discoveries = as.data.frame(cbind("d_BH"=d_BH, "d_StoBH"=d_StoBH, "d_Simes"=d_Simes,
                               "d_StoSimes"=d_StoSimes, "d_WMW"=d_WMW))
colnames(discoveries) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.discoveries = apply(discoveries, MARGIN = 2, FUN = mean)
  
powerGlobalNull = as.data.frame(cbind("d_BH"=d_BH>0, "d_StoBH"=d_StoBH>0, "d_Simes"=d_Simes>0,
                                        "d_StoSimes"=d_StoSimes>0, "d_WMW"=d_WMW>0))
colnames(powerGlobalNull) = c("BH", "BHSto", "CTSim", "CTSimSto", "CTWMW")
mean.powerGlobalNull = apply(powerGlobalNull, MARGIN = 2, FUN = mean)

prova.d_WMW = mean(d_WMW>0)
prova.resU = mean(resU)
  

boxplot(discoveries, main="Digits | Distribution of the number of discoveries")
points(x=1:5, y=mean.discoveries, pch=19, col="red")
mean.discoveries
mean.powerGlobalNull
prova.d_WMW
prova.resU

res=list("prova.d_WMW"=prova.d_WMW, 
         "prova.resU"=prova.resU, 
         "resU" = resU, 
         "discoveries"=discoveries,
         "mean.discoveries" = mean.discoveries, 
         "powerGlobalNull"=powerGlobalNull,
         "mean.powerGlobalNull"=mean.powerGlobalNull, 
         "n1"=n1, 
         "alpha"=alpha)

resShuttle10 = res
save(resShuttle10,
     file="C:/Users/c.magnani9/Documents/nout/trials/RealData/PowerStudy/New&TidyNoSimuFunction/alpha0.2/resShuttle10")

```





### References 
[1] Bates, S., E. Candes, L. Lei, Y. Romano, and M. Sesia (2023). Testing for outliers with conformal p-values.
\textit{Annals of Statistics}, {\bf 51}, 149–178.




