---
title: "Power analysis on Credit Card dataset"
author: "Significance level 0.2"
output: pdf_document
date: '`r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(doSNOW)
library(foreach)
library(nout)
library(tictoc)
library(isotree)
library(readr)
library(R.matlab)


compact_results = function(res){
  resT=as.data.frame(t(res))

  discoveries = as.data.frame(cbind("d_BH"=unlist(resT$d_BH), 
                                  "d_StoBH"=unlist(resT$d_StoBH),
                                  "d_Sim"=unlist(resT$d_Sim),
                                  "d_StoSimes"=unlist(resT$d_StoSimes), 
                                  "d_WMW"=unlist(resT$d_WMW)))
  mean.discoveries = apply(discoveries, MARGIN = 2, FUN = mean)


  power.GlobalNull = as.data.frame(discoveries>0)
  mean.powerGlobalNull = apply(power.GlobalNull, MARGIN = 2, FUN = mean)

  return(list("discoveries" = discoveries, 
            "mean.discoveries" = mean.discoveries,
            "power.GlobalNull" = power.GlobalNull,
            "mean.powerGlobalNull" = mean.powerGlobalNull,
            "pi.not" = unlist(resT$pi.not),
            "uniques"=unlist(resT$uniques),
            "n1"=unlist(resT$n1),
            "alpha"=unlist(resT$alpha)))
}


```


The aim is to compare on Credit Card datasets the performance of three closed testing procedures, which respectively use Simes local test with and without Storey estimator for the proportion of true null hypotheses and Wilcoxon-Mann-Whitney local test.

We fix the train set on which we train the isolation forest algorithm and we generate $B=10^4$ calibration and test sets. For each $b=1,\ldots,B$ we compute the number of discoveries obtained by Benjamini-Hochberg procedure with and without Storey's estimator for the proportion of true null hypotheses, by closed testing using Simes local test with and without Storey's estimator and by closed testing using Wilcoxon-Mann-Whitney local test.




## Credit Card dataset
Credit Card dataset (available at https://www.kaggle.com/mlg-ulb/creditcardfraud) consists of $284807$ observations, among which $n_{inliers}=284315$ items are inliers and the remaining $n_{outliers}=492$ are outliers.
We will denote by $l,m,n$ respectively the train set, the calibration set and the test set size. And reproducing the same setting as in [1], we have that $m+l=n_{inliers}/2$, $m=min\{2000,l/2\}$ and $n=min\{2000, l/3\}$. Moreover, in order to have exact control of  type I errors at the significance level $\alpha=0.2.$ we require $\alpha=n/(m+1)$.
In the case of Credit Card dataset we obtain $l=132158, \hspace{2mm} m=9999, \hspace{2mm} n=2000$.

Load the data and set the parameters as described above.

```{r warning=FALSE, message=FALSE}

dataset = read_csv("~/nout/trials/RealData/Datasets/Dataset creditcard/creditcard.csv")
out_ind = which(dataset[,ncol(dataset)]==1)
in_ind = which(dataset[,ncol(dataset)]==0)

# Initializing parameters
set.seed(321)

B=10^4

l = 132158
m = 9999
n = 2000
myalpha = n/(m+1)

tr_ind = sample(in_ind, size = l)
in_ind2 = setdiff(in_ind, tr_ind)
tr = dataset[tr_ind,]
n_cpus = parallel::detectCores()
iso.fo = isotree::isolation.forest(tr, ndim = ncol(dataset), ntrees = 150, sample_size = 256,
                                   nthreads = n_cpus, scoring_metric = "depth", 
                                   output_score = TRUE)
isofo.model = iso.fo$model
mycrit = nout::critWMW(m = n, n = m, alpha = myalpha)

```





### All inliers
We now set the proportion of inliers equal to $1$, so that the number of outliers $n_1=0$.
```{r warning=FALSE, message=FALSE}
n1=0

cl <- makeCluster(parallel::detectCores())
clusterEvalQ(cl, {library(isotree)})
registerDoSNOW(cl)


res = foreach(b = 1:B, .combine=cbind) %dopar% {
  n0 = n - n1
  N = n0 + m
  in_index3 = sample(in_ind, size = N)
  cal_ind = in_index3[1:m]
  te_ind = in_index3[(m + 1):N]
  cal = dataset[cal_ind,]
  te = dataset[te_ind,]
  S_cal = isotree::predict.isolation_forest(isofo.model, cal, type = "score")
  S_te = isotree::predict.isolation_forest(isofo.model, te, type = "score")
  d_WMW = nout::d_mannwhitney(S_Y = S_te, S_X = S_cal, crit = mycrit)
  d_Sim = nout::d_Simes(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  StoSimes = nout::d_StoreySimes(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  d_StoSimes = StoSimes$d
  pi.not = StoSimes$pi.not
  d_BH = nout::d_benjhoch(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  d_StoBH = nout::d_StoreyBH(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  uniques = length(unique(c(S_cal, S_te)))
  return(list("d_BH" = d_BH,
              "d_StoBH" = d_StoBH,
              "d_Sim" = d_Sim,
              "d_StoSimes" = d_StoSimes,
              "d_WMW" = d_WMW,
              "uniques" = uniques,
              "n1" = n1,
              "pi.not" = pi.not,
              "alpha" = myalpha))
}

stopCluster(cl)


results = compact_results(res)

boxplot(results$discoveries, main="CreditCard | Distribution of the number of discoveries")
points(x=1:5, y=results$mean.discoveries, pch=19, col="red")
results$mean.discoveries
results$mean.powerGlobalNull

resCredit0 = results
save(resCredit0,
     file="~/nout/trials/RealData/PowerStudy/New!/alpha0.2/CreditCardOnly0.2/resCredit0")

```




### 10% outliers
We now set the proportion of inliers equal to $0.9$. Referring to Digits dataset we have that the number of inliers is $n_0=1800$ and the number of outliers is $n_1=200$.

```{r warning=FALSE, message=FALSE}

n1=round(0.1*n)

cl <- makeCluster(parallel::detectCores())
clusterEvalQ(cl, {library(isotree)})
registerDoSNOW(cl)

res = foreach(b = 1:B, .combine=cbind) %dopar% {
  n0 = n - n1
  N = n0 + m
  in_index3 = sample(in_ind, size = N)
  cal_ind = in_index3[1:m]
  tein_ind = in_index3[(m + 1):N]
  teout_ind = sample(out_ind, size = n1)
  cal = dataset[cal_ind,]
  te = dataset[c(tein_ind, teout_ind),]
  S_cal = predict.isolation_forest(isofo.model, cal, type = "score")
  S_te = predict.isolation_forest(isofo.model, te, type = "score")
  d_WMW = nout::d_mannwhitney(S_Y = S_te, S_X = S_cal, crit = mycrit)
  d_Sim = nout::d_Simes(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  StoSimes = nout::d_StoreySimes(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  d_StoSimes = StoSimes$d
  pi.not = StoSimes$pi.not
  d_BH = nout::d_benjhoch(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  d_StoBH = nout::d_StoreyBH(S_X = S_cal, S_Y = S_te, alpha = myalpha)
  uniques = length(unique(c(S_cal, S_te)))
  return(list("d_BH" = d_BH,
              "d_StoBH" = d_StoBH,
              "d_Sim" = d_Sim,
              "d_StoSimes" = d_StoSimes,
              "d_WMW" = d_WMW,
              "uniques" = uniques,
              "n1" = n1,
              "pi.not" = pi.not,
              "alpha" = myalpha))

}

stopCluster(cl)

results = compact_results(res)

boxplot(results$discoveries, main="CreditCard | Distribution of the number of discoveries")
points(x=1:5, y=results$mean.discoveries, pch=19, col="red")
results$mean.discoveries
results$mean.powerGlobalNull

resCredit10 = results
save(resCredit10,
     file="~/nout/trials/RealData/PowerStudy/New!/alpha0.2/CreditCardOnly0.2/resCredit10")

```


